Comment: Reasoning about Interference Between Units

### 2015-11-10 paper/paper.tex
Revealing our names
Fixing typos

\begin{titlepage}

\maketitle

\begin{abstract} 
\citet{bowers2013sutva} showed that one could use Fisher's randomization-based
hypothesis testing framework to assess counterfactual causal models of
treatment propagation and spillover across social networks.  This research
note improves the statistical infernce presented in \citet{bowers2013sutva}
(henceforth BFP) by substituting a test statistic based on a sum of squared
residuals and incorporating information about the fixed network for the simple
Kolmogorov-Smirnov test statistic  \citep[\S 5.4]{MylesHollander1999a}
they used. This note incrementally improves
the application of BFP's ``reasoning about interference'' approach. We do not
offer general results about test statistics for multi-parameter causal models on social
networks here, but instead hope to stimulate further,
and deeper, work on test statistics and sharp hypothesis testing.
\end{abstract}

>>>>

\begin{titlepage}
\maketitle
\thispagestyle{empty}

\begin{abstract} 
\citet{bowers2013sutva} showed that one could use Fisher's randomization-based
hypothesis testing framework to assess counterfactual causal models of
treatment propagation and spillover across social networks.  This research
note improves the statistical inference presented in \citet{bowers2013sutva}
(henceforth BFP) by substituting a test statistic based on a sum of squared
residuals and incorporating information about the fixed network for the simple
Kolmogorov-Smirnov test statistic  \citep[\S 5.4]{MylesHollander1999a}
they used. This note incrementally improves
the application of BFP's ``reasoning about interference'' approach. We do not
offer general results about test statistics for multi-parameter causal models on social
networks here, but instead hope to stimulate further,
and deeper, work on test statistics and sharp hypothesis testing.
\end{abstract}
